---
title: "RWorksheet_Deluna#4c"
author: "Nicole De Luna"
date: "2023-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. a. Show your solutions on how to import a csv file into the environment.
```{r}
library(readr)
mpg <- read_csv("mpg.csv")

View(mpg)
```


1b. Which variables from mpg dataset are categorical?
```{r}
ctgr <- names(sapply(mpg, is.factor))
print(ctgr)

```

1c. Which are continuous variables?
```{r}
conti <- names(sapply(mpg, is.numeric))
print(conti)
```


#2. Which manufacturer has the most models in this data set? Which model has the most variations? Show your answer.
```{r}
  model <- mpg %>%
  group_by(manufacturer) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

print(model)

#Dodge is the manufacturer with the most models.
count <- mpg %>%
  group_by(model) %>%
  summarise(variation = n()) %>%
  arrange(desc(variation))

print(count)
#Caravan 2wd is the model with the most variation.
```



2 a
```{r}
model <- unique(mpg[, c("manufacturer", "model")])
count <- table(model$manufacturer) 
print(count)
```


2 b
```{r}
ggplot(mpg, aes(x = model, y = manufacturer, color = class)) +
  geom_point() +
  labs(title = "Car models and manufacturers",
       x = "Car model",
       y = "Manufacturer",
       color = "Vehicle class",
       caption = "Source: Your Data Source") +
  theme_minimal() +
  theme(legend.position = "right")

```


2. Same dataset will be used. You are going to show the relationship of the model and the manufacturer

```{r}


```